---
title: "Assignment 1"
author: "Josep Franquet & Lidia Montero"
date: "11/10/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data loading

First, set working directory has to be fixed:

```{r}
setwd("~/Desktop/SIM/Assignment_car") #Set working directory
```

This data dictionary describes data  (https://www.kaggle.com/adityadesai13/used-car-dataset-ford-and-mercedes) - A sample of 5000 trips has been randomly selected from Mercedes, BMW, Volkwagen and Audi manufacturers. So, firstly you have to combine used car from the 4 manufacturers into 1 dataframe.

The cars with engine size 0 are in fact electric cars, nevertheless Mercedes C class, and other given cars are not electric cars,so data imputation is requered. 


  -   manufacturer	Factor: Audi, BMW, Mercedes or Volkswagen
  -   model	Car model
  -   year	registration year
  -   price	price in £
  -   transmission	type of gearbox
  -   mileage	distance used
  -   fuelType	engine fuel
  -   tax	road tax
  -   mpg	Consumption in miles per gallon   
  -   engineSize	size in litres

Data loading and union:

```{r}
# Lecture of DataFrames:
df1 <- read.table("audi.csv",header=T, sep=",")
df1$manufacturer <- "Audi"
df2 <- read.table("bmw.csv",header=T, sep=",")
df2$manufacturer <- "BMW"
df3 <- read.table("merc.csv",header=T, sep=",")
df3$manufacturer <- "Mercedes"
df4 <- read.table("vw.csv",header=T, sep=",")
df4$manufacturer <- "VW"

# Union by row:
df <- rbind(df1,df2,df3,df4)
dim(df)  # Size of data.frame
str(df) # Object class and description
names(df) # List of variable names

### Use birthday of 1 member of the group as random seed:
set.seed(110600)
# Random selection of x registers:
sam<-as.vector(sort(sample(1:nrow(df),1000)))
head(df)  # Take a look to the first rows/instances (6 rows)
df<-df[sam,]  # Subset of rows _ It will be my sample
summary(df)

#Keep information in an .Rdata file:
save(list=c("df"),file="MyOldCars-Raw.RData")

```

After all treatment, you should find a DataFrame with the following characteristics:

```{r}
# Clean workspace
rm(list=ls())

filepath<-"~/Desktop/SIM/Assignment_car/"
#load(paste0(filepath,"MyOldCars-1000Clean.RData"))
```

Useful functions for the development of your assignment:

```{r}
# Some useful functions
calcQ <- function(x) {
  s.x <- summary(x)
  iqr<-s.x[5]-s.x[2]
  list(souti=s.x[2]-3*iqr, mouti=s.x[2]-1.5*iqr, min=s.x[1], q1=s.x[2], q2=s.x[3], 
       q3=s.x[5], max=s.x[6], mouts=s.x[5]+1.5*iqr, souts=s.x[5]+3*iqr ) }

countNA <- function(x) {
  mis_x <- NULL
  for (j in 1:ncol(x)) {mis_x[j] <- sum(is.na(x[,j])) }
  mis_x <- as.data.frame(mis_x)
  rownames(mis_x) <- names(x)
  mis_i <- rep(0,nrow(x))
  for (j in 1:ncol(x)) {mis_i <- mis_i + as.numeric(is.na(x[,j])) }
  list(mis_col=mis_x,mis_ind=mis_i) }

countX <- function(x,X) {
  n_x <- NULL
  for (j in 1:ncol(x)) {n_x[j] <- sum(x[,j]==X) }
  n_x <- as.data.frame(n_x)
  rownames(n_x) <- names(x)
  nx_i <- rep(0,nrow(x))
  for (j in 1:ncol(x)) {nx_i <- nx_i + as.numeric(x[,j]==X) }
  list(nx_col=n_x,nx_ind=nx_i) }
```

Useful functions for your packages treatment:

```{r message=FALSE, warning=FALSE}
# Introduce required packages:
requiredPackages <- c("effects","FactoMineR","car", "factoextra","RColorBrewer","ggplot2","dplyr","ggmap","ggthemes","knitr")

#use this function to check if each package is on the local machine
#if a package is installed, it will be loaded
#if any are not, the missing package(s) will be installed and loaded
package.check <- lapply(requiredPackages, FUN = function(x) {
  if (!require(x, character.only = TRUE)) {
    install.packages(x, dependencies = TRUE)
    library(x, character.only = TRUE)
  }
})
#verify they are loaded
# search()
```

